Global case

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

	\subsection{Improvement of the simplified model}
	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed. (This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)

@@

>>>>

	\subsection{Improving the Accuracy of the Simplified Model}
	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed. (This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)

@@

	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables. Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
